Supporting information for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-12-15 docs/cover_letter.tex
Big directory rename, plus more PNAS changes.

\documentclass{jpmletter}

@@

    \opening{Dear Editorial Board of Nature,}

    Please find enclosed our manuscript ``Effectiveness of UNAIDS
    targets and HIV vaccination across 127 countries,'' which we are
    submitting to \textit{Nature} as a Letter.

@@

    We believe our letter will be approximately 4 pages when
    formatted.

>>>>

\documentclass[12pt]{jpmletter}

@@

    \opening{Dear Editorial Board,}

    Please find enclosed our manuscript ``Effectiveness of UNAIDS
    targets and HIV vaccination across 127 countries,'' which we are
    submitting to \textit{PNAS}.

@@

### 2016-12-15 docs/supporting_information.tex
Big directory rename, plus more PNAS changes.

\usepackage{xr}
\externaldocument{extended_data_fig_1}

\newcommand{\md}{\mathrm{d}}
\DeclareMathOperator{\Uniform}{Uniform}
\DeclareMathOperator{\Triangular}{Triangular}
\DeclareMathOperator{\Lognormal}{Lognormal}
\DeclareMathOperator{\BetaPERT}{Beta-PERT}

@@

We developed a mathematical model of HIV transmission and progression
that stratifies HIV infection into acute, chronic undiagnosed, chronic
diagnosed, chronic treated, chronic virally suppressed, and AIDS,
along with uninfected unvaccinated and vaccinated people
(\autoref{model} \& \autoref{model_diag}), tailored to
each of 127 countries.  Simulations of our model project the number of
people in each HIV stratum from 2015 to 2035, from which statistics
such as prevalence and incidence were calculated.  To evaluate the
impact of the 90--90--90 and 95--95--95 UNAIDS goals, model transition
rates were adjusted dynamically to meet intervention goals for
diagnosis, treatment, viral suppression, and vaccination coverage
(\autoref{targets}).  Data and estimates from many sources, including
The World Bank and UNAIDS, were used to parametrize the model
(\autoref{data_sources}).  Country-specific transmission rates were
fitted to estimates of the historical trajectories of incidence and
prevalence, spanning from as early as 1990 for some countries
(\autoref{model_fitting}). For every scenario of intervention
combinations, we conducted 1000 model simulations, sampling values of
model parameters from empirical distributions for each simulation, and
reported the results with median and percentiles
(\autoref{uncertainty}).

@@

Transitions between model states are governed by a system of
differential equations parametrized using values found in other
studies, along with transmission rates derived from UNAIDS estimates
of incidence and prevalence (\autoref{model_param}).  The model is
deterministic, but uncertainty in the parameters was treated by
running the model 1000 times with samples from the parameter
distributions (\autoref{uncertainty}) and summarizing the model
outcomes using the median and percentiles.  Each country was modeled
separately (Extended Data
Figs.~\ref*{effectiveness_Afghanistan}--\ref*{effectiveness_Zimbabwe})
and the country simulations were aggregated to calculate global and
regional outcomes (Extended Data
Figs.~\ref*{effectiveness_Global}--\ref*{effectiveness_Western_Europe}).

@@

\begin{figure}
  \begin{center}
    \input{../Codes/plots/transmission_rate.pgf}
  \end{center}
  \caption{Country-specific distributions of transmission rate,
    $\bar{\beta}$, calculated based on UNAIDS historical estimates of
    country prevalence and incidence.  See \autoref{model_fitting}.}
  \label{transmission_rate}
\end{figure}

@@

\begin{figure}
   \centering
   \input{../Codes/plots/prcc.pgf}
   \caption{Sensitivity of global HIV incidence from 2015 to 2035 to
     model parameters.  Left is the sensitivity of infections averted
     by 95--95--95, relative to status quo.  Right is the sensitivity
     of vaccination with status quo levels of diagnosis and treatment,
     relative to status quo.  Sensitivity is measured by the partial
     rank correlation coefficient (PRCC).}
   \label{PRCCs}
\end{figure}

@@

\item[Beta-PERT] was used for the efficacy of viral suppression at
  reducing transmission, $\epsilon$, because the confidence interval
  had an extremely long right tail \cite{Donnell2010-xo}, which would
  strongly skew the mean and median of a Triangular distribution to
  the right.  $\BetaPERT(a, b, c)$, the Beta-PERT probability
  distribution \cite{malcom1959} with minimum $a$, mode $b$, and
  maximum $c$, has density function
  \begin{equation}
    \label{BetaPERT}
    f_{\BetaPERT}(x) =
    \begin{cases}
      \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} B(v, w)}
      & \text{if $a \leq x \leq c$,}
      \\
      0 & \text{otherwise,}
    \end{cases}
  \end{equation}
  where
  \begin{equation}
    \begin{split}
      \mu &= \frac{a + \lambda b + c}{\lambda + 2},
      \\
      v &= \frac{(\mu - a)(2 b - a - c)}{(b - \mu) (c - a)},
      \\
      w &= \frac{v (a - \mu)}{\mu - c},
    \end{split}
  \end{equation}
  and $B(v, w)$ is the standard beta function
  \cite[\S6.2]{davis1972}.
  We used the standard value of $\lambda = 4$.

@@

>>>>

\newcommand{\md}{\mathrm{d}}
\DeclareMathOperator{\Uniform}{Uniform}
\DeclareMathOperator{\Triangular}{Triangular}
\DeclareMathOperator{\Lognormal}{Lognormal}
\DeclareMathOperator{\BetaPERT}{Beta-PERT}
\DeclareMathOperator{\Beta}{B}

@@

We developed a mathematical model of HIV transmission and progression
that stratifies HIV infection into acute, chronic undiagnosed, chronic
diagnosed, chronic treated, chronic virally suppressed, and AIDS,
along with uninfected unvaccinated and vaccinated people
(\autoref{model} \& \autoref{model_diag}), tailored to each of 127
countries.  Simulations of our model project the number of people in
each HIV stratum from 2015 to 2035, from which statistics such as
prevalence and incidence were calculated.  To evaluate the impact of
the 90--90--90 and 95--95--95 UNAIDS goals, model transition rates
were adjusted dynamically to meet intervention goals for diagnosis,
treatment, viral suppression, and vaccination coverage
(\autoref{targets}).  Data and estimates from many sources, including
The World Bank and UNAIDS, were used to parametrize the model
(\autoref{data_sources}).  Country-specific transmission rates were
fitted to estimates of the historical trajectories of incidence and
prevalence, spanning from as early as 1990 for some countries
(\autoref{model_fitting}). For every scenario of intervention
combinations, we conducted 1000 model simulations, sampling values of
model parameters from empirical distributions for each simulation, and
reported the results with median and percentiles
(\autoref{uncertainty}).  The effectiveness of the UNAIDS goals and
vaccination was estimated for each of the 127 countries and aggregated
by region and globally (\autoref{effectiveness_all_plots}).

@@

Transitions between model states are governed by a system of
differential equations parametrized using values found in other
studies, along with transmission rates derived from UNAIDS estimates
of incidence and prevalence (\autoref{model_param}).  The model is
deterministic, but uncertainty in the parameters was treated by
running the model 1000 times with samples from the parameter
distributions (\autoref{uncertainty}) and summarizing the model
outcomes using the median and percentiles.  Each country was modeled
separately
(\hyperref[effectiveness_Afghanistan]{Figs.~\ref*{effectiveness_Afghanistan}}--\ref{effectiveness_Zimbabwe})
and the country simulations were aggregated to calculate global and
regional outcomes
(\hyperref[effectiveness_Global]{Figs.~\ref*{effectiveness_Global}}--\ref*{effectiveness_Western_Europe}).

@@

\begin{figure}
  \begin{center}
    \input{../src/plots/transmission_rate.pgf}
  \end{center}
  \caption{Country-specific distributions of transmission rate,
    $\bar{\beta}$, calculated based on UNAIDS historical estimates of
    country prevalence and incidence.  The colored shapes are the
    sampling distributions and the black bars are the modes of these
    distributions.  See \autoref{model_fitting}.}
  \label{transmission_rate}
\end{figure}

@@

\begin{figure}
   \centering
   \input{../src/plots/prcc.pgf}
   \caption{Sensitivity of global HIV incidence from 2015 to 2035 to
     model parameters.  Left is the sensitivity of infections averted
     by 95--95--95, relative to status quo.  Right is the sensitivity
     of vaccination with status quo levels of diagnosis and treatment,
     relative to status quo.  Sensitivity is measured by the partial
     rank correlation coefficient (PRCC).}
   \label{PRCCs}
\end{figure}

@@

\item[Beta-PERT] was used for the efficacy of viral suppression at
  reducing transmission, $\epsilon$, because the confidence interval
  had an extremely long right tail \cite{Donnell2010-xo}, which would
  strongly skew the mean and median of a Triangular distribution to
  the right.  $\BetaPERT(a, b, c)$, the Beta-PERT probability
  distribution \cite{malcom1959} with minimum $a$, mode $b$, and
  maximum $c$, has density function
  \begin{equation}
    \label{BetaPERT}
    f_{\BetaPERT}(x) =
    \begin{cases}
      \frac{(x - a)^{v - 1} (c - x)^{w - 1}}{(c - a)^{v + w - 2} \Beta(v, w)}
      & \text{if $a \leq x \leq c$,}
      \\
      0 & \text{otherwise,}
    \end{cases}
  \end{equation}
  where
  \begin{equation}
    \begin{split}
      \mu &= \frac{a + \lambda b + c}{\lambda + 2},
      \\
      v &= \frac{(\mu - a)(2 b - a - c)}{(b - \mu) (c - a)},
      \\
      w &= \frac{v (a - \mu)}{\mu - c},
    \end{split}
  \end{equation}
  and $\Beta(v, w)$ is the standard beta function
  \cite[\S6.2]{davis1972}.
  We used the standard value of $\lambda = 4$.

@@

\newpage
\vspace*{3in}
\section{Global, regional, and per-country effectiveness}
\label{effectiveness_all_plots}
\newpage

\input{../src/plots/effectiveness_all/all}
